---
title: "Modelos lineares aula 1"
author: "Danilo de Paula Santos"
date: "17/10/2019"
output: html_document
---

```{r preparação do R}

# install.packages("compareGroups")
# install.packages("ggplot2")
# install.packages("data.table")


library("compareGroups")
library("ggplot2")
library("haven")

```

# Estuda da relação entre infecção por acilóstomo e perda de sangue. Tailândia 1970

```{r carregando suwit}

suwit <- read_sav("C:/Users/00265021/Documents/Cadeiras/Modelos lineares/Suwit.sav")

```

```{r descritiva suwit}

compare_suwit <- compareGroups( ~ ., data = suwit)

summary(compare_suwit)
```

```{r tabela suwit}

createTable(compare_suwit)
```


# Estudo Fat_dat "Fitting Percentage of Body Fat to Simple Body Measurements"


```{r carregando fat_dat}

fat_dat <- read_sav("C:/Users/00265021/Documents/Cadeiras/Modelos lineares/fat_dat.sav")

```

Corrigindo os erros de digitação:

- The body densities for cases 48, 76, and 96, for instance, each seem to have one digit in error as can be seen from the two body fat percentage values.
- Case 42) over 200 pounds in weight who is less than 3 feet tall (the height should presumably be 69.5 inches, not 29.5 inches)!
- The percent body fat estimates are truncated to zero when negative (case 182)

```{r corrigindo fat_dat}
# Altura

fat_dat2$altura_pol <- ifelse( fat_dat2$numero == 42, 69.5, fat_dat2$altura_pol)

# Densidades

fat_dat2$densidade <- ifelse( fat_dat2$numero == 48, 1.0865, fat_dat2$densidade)
fat_dat2$densidade <- ifelse( fat_dat2$numero == 76, 1.0566, fat_dat2$densidade)
fat_dat2$densidade <- ifelse( fat_dat2$numero == 96, 1.0591, fat_dat2$densidade)

```



```{r descritivas fat_dat}
compare_fat <- compareGroups( ~ ., data = fat_dat2)

summary(compare_fat)
```


```{r tabela fat_dat}

createTable(compare_fat)

```

```{r normalidade fat_dat }

plot(compare_fat)

```

```{r dispersão fat_dat }

ggplot(fat_dat2, aes(x = imc, y = fat_Brozek))+
  geom_point() +
  theme_minimal()

```

```{r regressão fat_dat }

ggplot(fat_dat2, aes(x = imc, y = fat_Brozek))+
  geom_point() +
  theme_minimal()

```